---
title: "1LBKA"
author: "Claudia Ki"
date: "11/30/2021"
output: html_document
---
1) Use a LM to fit BKA data for first LPS challenge, doesn't work because data is not normal
2) Use a GLM with a logit link for the beta distribution as it can be bimodal and fit proportion data (%) well (logit link)
3) Use a GLMM with a logit link since we have repeated measures and want to include time as a predictor
3a) Change all 0s to 0.000001 something insignificant to make it easier to work with "0s" in the model 










Check for interactions using mixed model anova
```{r}
gi <- read.csv("C:/Users/claud/OneDrive - USU/Desktop/ASU green iguana 2021/greeniguanaAnalysis/modData/BKA1LPSlong.csv")
View(gi)
#install.packages("tidyverse")
#install.packages("rstatix")
#install.packages("ggpubr")
library("rstatix")
library("tidyverse")
library("dplyr")
library("ggpubr")
gi$time <- as.factor(gi$time) #convert to factor for the aov
gi$iguanaID <- as.factor(gi$iguanaID)

```

# Mixed model anova
``` {r}
BKAaov <- anova_test(
  data = gi, dv = bka, wid = iguanaID,
  between = c(diet, lps), within = time
)
get_anova_table(BKAaov)
```
Interaction of diet and LPS, main effect of time and diet. 

pairwise is next step...

