---
title: "dROM"
author: "Claudia Ki"
date: "1/25/2022"
output: html_document
---
Green iguana analysis report on dROM from both challenges

```{r setup, include=FALSE}
gi <- read.csv("C:/Users/claud/OneDrive - USU/Desktop/ASU green iguana 2021/greeniguanaAnalysis/modData/dromLong.csv")
View(gi) #note that all NA rows were omitted automatically during the transposal
library("rstatix")
library("tidyverse")
library("dplyr")
library("ggpubr")
str(gi)
gi$time <- as.factor(gi$time)
gi$iguanaID <- as.factor(gi$iguanaID)
gi$tx <- as.factor(gi$tx)
gi$diet <- as.factor(gi$diet)
gi$lps <- as.factor(gi$lps)
str(gi)
```
First LPS Challenge
```{r}
data <- gi %>%
  filter(time %in% c("0423dromstd","0428dromstd", "0430dromstd", "0504dromstd", "0511dromstd","0525dromstd")) 
anova_test(
  data = data, dv = drom, wid = iguanaID,
  between = c(diet, lps), within = time) 
data %>%
  group_by(time) %>%
  pairwise_t_test(
    drom ~ lps, paired = FALSE, 
    p.adjust.method = "bonferroni") 
simpleMainEffect <- data %>%
  group_by(time) %>%
  anova_test(dv = drom, wid = iguanaID, between = lps) %>%
  get_anova_table() %>%
  adjust_pvalue(method = "bonferroni")
simpleMainEffect
```
Second LPS Challenge
```{r}
data2 <- gi %>%
  filter(time %in% c("0525dromstd","0528dromstd", "0530dromstd", "0603dromstd", "0610dromstd","0624dromstd")) 
anova_test(
  data = data2, dv = drom, wid = iguanaID,
  between = c(diet, lps), within = time) 
simpleMainEffect <- data2 %>%
  group_by(time) %>%
  anova_test(dv = drom, wid = iguanaID, between = diet) %>%
  get_anova_table() %>%
  adjust_pvalue(method = "bonferroni")
simpleMainEffect

```

# Summary of First Challenge
1) Main effect of diet (glucose higher dROM)
2) Interaction effect of LPS and time 
  a)0525, control lower dROM than LPS


# Summary of Second Challenge
1) Main effect of diet (glucose higher dROM)
2) Main effect of LPS (LPS higher dROM)
3) Interaction effect of diet and time
  a) 0525 glucose higher dROM
  b) 0610 glucose higher dROM
  c) 0624 water higher dROM