---
title: "Glycerol"
author: "Claudia Ki"
date: "2/28/2022"
output: html_document
---
Green iguana analysis report on glycerol from both challenges

```{r setup, include=FALSE}
gi <- read.csv("C:/Users/claud/OneDrive - USU/Desktop/ASU green iguana 2021/greeniguanaAnalysis/modData/glycerolLong.csv")
library("rstatix")
library("tidyverse")
library("dplyr")
library("ggpubr")
str(gi)
gi$time <- as.factor(gi$time)
gi$iguanaID <- as.factor(gi$iguanaID)
gi$tx <- as.factor(gi$tx)
gi$diet <- as.factor(gi$diet)
gi$lps <- as.factor(gi$lps)
str(gi)

data <- gi %>%
  filter(time %in% c("0423gly","0428gly", "0430gly", "0504gly", "0511gly","0525gly")) 
data <- data %>%
  mutate(gly_inflog =  log(glycerol+0.0001))            # data was inflatd by 0.0001 to avoid inf when logged
data <- data %>%
  filter(gly_inflog > -5)          #got rid of massive outlier (10x the avg)

data2 <- gi %>%
  filter(time %in% c("0525gly","0528gly", "0530gly", "0603gly", "0610gly","0624gly")) 
data2<- data2 %>%
  mutate(gly_inflog = log(glycerol +0.0001))
          # inflate and log data in the same way 
```
Note* Data was logged and inflated by 0.0001 for normality (outlier was also taken out, more than 10x avg)

Primary LPS Challenge
```{r}
anova_test(
  data = data, dv = gly_inflog, wid = iguanaID,
  between = c(diet, lps), within = time) 

data %>%
  group_by(diet) %>%
  get_summary_stats(glycerol, type = "mean_se")    # used data$glycerol and not data$gly_inflog 

data %>%
  pairwise_t_test(
    gly_inflog ~ time, paired = FALSE, 
    p.adjust.method = "bonferroni"
  )

```

#Secondary LPS Challenge
```{r}
anova_test(
  data = data2, dv = glycerol, wid = iguanaID,
  between = c(diet, lps), within = time) 

data2 %>%
  group_by(diet) %>%
  get_summary_stats(glycerol, type = "mean_se")

data2 %>%
  group_by(time) %>%
  get_summary_stats(glycerol, type = "mean_se")

data2 %>%
  pairwise_t_test(
    glycerol ~ time, paired = FALSE, 
    p.adjust.method = "bonferroni"
  )

```
# Summary of Primary Challenge
1) Main effect of diet (glucose higher)
2) Main effect of time
 a) 0504 and 0428, 0430
 b) 0511 and 0423, 0428, 0430
 c) 0525 and 0423, 0428, 0430

# Summary of Secondary Challenge
1) Main effect of diet (glucose higher)
2) Main effect of time (0528 and 0624)
3) interaction diet:time
4) interaction lps:time (but not signficant in post hoc)
