---
title: "Total TRI"
author: "Claudia Ki"
date: "2/24/2022"
output: html_document
---
Green iguana analysis report on total triglycerides (glycerol and true triglycerides) from both challenges

```{r setup, include=FALSE}

gi <- read.csv("C:/Users/claud/OneDrive - USU/Desktop/ASU green iguana 2021/greeniguanaAnalysis/modData/triLong.csv")
View(gi) #note that all NA rows were omitted automatically during the transposal
library("rstatix")
library("tidyverse")
library("dplyr")
library("ggpubr")
str(gi)
gi$time <- as.factor(gi$time)
gi$iguanaID <- as.factor(gi$iguanaID)
gi$tx <- as.factor(gi$tx)
gi$diet <- as.factor(gi$diet)
gi$lps <- as.factor(gi$lps)
str(gi)

data <- gi %>%
  filter(time %in% c("0423totri","0428totri", "0430totri", "0504totri", "0511totri","0525totri")) 
hist((data$totri)) #data is normal
data2 <- gi %>%
  filter(time %in% c("0525totri","0528totri", "0530totri", "0603totri", "0610totri","0628totri")) 
hist((data$totri))
```
First LPS Challenge
```{r}
anova_test(
  data = data, dv = totri, wid = iguanaID,
  between = c(diet, lps), within = time) 

data %>%
  group_by(diet) %>%
  get_summary_stats(totri, type = "mean_se")

data %>%
  pairwise_t_test(
    totri ~ time, paired = FALSE, 
    p.adjust.method = "bonferroni"
  )

data %>%
  group_by(time) %>%
  anova_test(dv = totri, wid = iguanaID, between = lps) %>%
  get_anova_table() %>%
  adjust_pvalue(method = "bonferroni")

data %>%
  group_by(lps, time) %>%
  get_summary_stats(totri, type = "mean_se")

```
Second LPS Challenge
```{r}
anova_test(
  data = data2, dv = totri, wid = iguanaID,
  between = c(diet, lps), within = time) 

data2 %>%
  group_by(diet) %>%
  get_summary_stats(totri, type = "mean_se")

data2 %>%
  pairwise_t_test(
    totri ~ time, paired = FALSE, 
    p.adjust.method = "bonferroni"
  )

data2 %>%
  group_by(time) %>%
  anova_test(dv = totri, wid = iguanaID, between = lps) %>%
  get_anova_table() %>%
  adjust_pvalue(method = "bonferroni")

data2 %>%
  group_by(time) %>%
  anova_test(dv = totri, wid = iguanaID, between = diet) %>%
  get_anova_table() %>%
  adjust_pvalue(method = "bonferroni")

data2 %>%
  group_by(diet, time) %>%
  get_summary_stats(totri, type = "mean_se")
```

# Summary of First Challenge
1) Main effect of diet (glucose higher)
2) Main effect of time 
   a) 0428 (24hr post) and 0504 (1week), 0511(2week), 0525(4week)
   b) 0511 (2 week) and 0423 (preLPS), 0430(72)
3) Interaction LPS:time (0428 control higher than LPS)

# Summary of Second Challenge
1) Main effect of diet (glucose higher)
2) Main effect of time
   a) 0528 (24hr post) and 0603 (1wk), 0610 (2wk), 0628 (4wk)
   b) 0530 (72hr post) and 0603 (1wk), 0610 (2wk), 0628 (4wk)
3) Interaction diet:time
   a) diet significant at every time point (glucose is always higher)
4) Interaction LPS:time (not actually significant with post hoc)